API design for machine learning software: experiences from the scikit-learn project

### 2013-08-09 paper.tex
Weka and Orange offer an API

Recent years have witnessed a rising interest in machine learning and data
mining with applications in many fields. With this rise comes a host of machine
learning packages (both open source and proprietary) with which \sklearn
competes. Some of those, including Weka~\citep{hall2009weka} or
Orange~\citep{Demsar2004}, offer and focus on a graphical user interface (GUI)
which allows novices to easily use and apply machine learning algorithms. By
contrast, the target audience of \sklearn is capable of programming, and
therefore we focus on developing a usable and consistent API, rather than expend
effort into creating a GUI\@. In addition, while GUIs are useful tools, they
sometimes make reproducibility difficult in the case of complex workflows
(although those packages usually have developed a GUI for managing complex
tasks).

>>>>

Recent years have witnessed a rising interest in machine learning and data
mining with applications in many fields. With this rise comes a host of machine
learning packages (both open source and proprietary) with which \sklearn
competes. Some of those, including Weka~\citep{hall2009weka} or
Orange~\citep{Demsar2004}, offer APIs but actually focus on the use of a graphical user interface (GUI)
which allows novices to easily apply machine learning algorithms. By
contrast, the target audience of \sklearn is capable of programming, and
therefore we focus on developing a usable and consistent API, rather than expend
effort into creating a GUI\@. In addition, while GUIs are useful tools, they
sometimes make reproducibility difficult in the case of complex workflows
(although those packages usually have developed a GUI for managing complex
tasks).
